\documentclass[11pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{
 a4paper,
 right=14mm,
 bottom=20mm,
 top=18mm,
}

\lstset{
    frame=single,
    breaklines=true,
    postbreak=\raisebox{0pt}[0pt][0pt]{\ensuremath{\hookrightarrow\space}},
    basicstyle=\ttfamily,
    showstringspaces=false,
}
 
\renewcommand{\chaptername}{Program}

\title{Lab Sheet 02 \\
      \textbf{C Programming} \\
      CSC-110}
\author{\textbf{Anukul Adhikari} \\ 11/24/2076}
\date{\today}

\begin{document}
\maketitle

\chapter*{Information}
All code used in this report including source code of this report itself is available at:\\ \texttt{https://github.com/beinganukul/Lab-Sheet-CSC110}
\section*{Software}
Following compiler and configuration is verified to work with the snippets in this report:\\
\texttt{Compiler - gcc version 9.2.1 20200130\\
Compiler target - Arch Linux 9.2.1+20200130-2
}

\tableofcontents

\chapter{Fibonacci Series}
\section{Problem Statement}
Write a program to generate Fibonacci Series.
\section{Program}
\lstinputlisting[language=c]{01-fibonacci-series.c}

\chapter{Armstrong Number}
\section{Problem Statement}
Write a program to print out all the armstrong number between $1$ to $100$.
\section{Program}
\lstinputlisting[language=c]{02-armstrong-number.c}

\chapter{While Loop}
\section{Problem Statement}
Write a program to generate numbers from 1 to 10 using while loop.
\section{Program}
		\lstinputlisting[language=c]{04-1-10-while.c}

\chapter{While Loop}
\section{Problem Statement}
Write a program to generate numbers from 9 to 0 using while loop.
\section{Algorithm}
\section{Program}
\lstinputlisting[language=c]{05-9-0-while.c}

\chapter{While Loop}
\section{Problem Statement}
Write a program to print all the numbers from 10 to 1 and find their sum using while loop.
\section{Program}
\lstinputlisting[language=c]{06-sum-from-10-1.c}

\chapter{Factorial}
\section{Problem Statement}
Write a program to calculate factorial of a given number.
\section{Program}
\lstinputlisting[language=c]{07-factorial.c}
		

\chapter{Counting Cases}
\section{Problem Statement}
Write a program to enter the numbers till the user wants and at the end it should display the count of positive,negative and zeros.
\section{Program}
\lstinputlisting[language=c]{08-po-ne-ze.c}

\chapter{Pattern Generation}
\section{Problem Statement}
Write a program to generate following output
		$\\*****$
		$\\****$
		$\\***$
		$\\**$
		$\\*$
\section{Program}
\lstinputlisting[language=c]{09-star.c}

\chapter{Multiplication Table}
\section{Problem Statement}
Write a program to display Multiplication table from 1 to 10.
\section{Program}
\lstinputlisting[language=c]{10-multiplication-table.c}

\chapter{Square or Cube}
\section{Problem Statement}
Write a program to display square of given number if it is odd and cube if it is even.
\section{Program}
\lstinputlisting[language=c]{11-square-cube.c}
        
\chapter{Raised to the Power}
\section{Problem Statement}
Two numbers are entered through the keyboard.Write a program to find the value of one number raise to the power of another.
\section{Program}
\lstinputlisting[language=c]{12-raised-power.c}

\chapter{Product of Digits}
\section{Problem Statement}
Write a program to find the product of digits of any number.
\section{Program}
\lstinputlisting[language=c]{13-product-of-digits.c}

\chapter{Sum of Digits}
\section{Problem Statement}
Write a program to find the sum of digits of any number.
\section{Program}
\lstinputlisting[language=c]{14-sum-of-digits.c}


\end{document}
